\section*{Executive Summary}
This report provides an in-depth analysis of IBM's technology management practices, including its historical background, current state of technology infrastructure and capabilities, and best practices in technology management. The report also highlights the implications of IBM's findings and provides recommendations for the company to maintain its leadership position in key technology areas.

IBM is a technology company that has been at the forefront of innovation for over a century. The company's technology initiatives have evolved over time, from tabulating machines to mainframes, personal computers, and cloud computing. IBM's current technology infrastructure and capabilities include hybrid cloud, artificial intelligence (AI), blockchain, quantum computing, and cybersecurity.

IBM's technology management practices are guided by best practices that include a focus on innovation, collaboration, and customer-centricity. The company invests heavily in research and development to maintain its leadership position in key technology areas. IBM also has a strong brand reputation and develops targeted marketing and sales strategies for key customer segments.

The implications of IBM's findings are significant. The company needs to continue investing in research and development to maintain its leadership in key technology areas. IBM should also expand its global reach to tap into new markets and customer segments. Strengthening brand reputation and developing targeted marketing and sales strategies for key customer segments are also essential.

To maintain its leadership position in key technology areas, IBM should invest in hybrid cloud and AI, two of the fastest-growing IT segments. Hybrid cloud is a critical area for IBM, as it enables customers to seamlessly integrate their on-premises and cloud environments. AI is another rapidly growing IT segment that IBM should continue to invest in to maintain its leadership position in this market.

IBM should also focus on developing its blockchain and quantum computing capabilities. Blockchain is a distributed ledger technology that has the potential to transform industries such as finance, healthcare, and supply chain management. Quantum computing is a new computing paradigm that has the potential to solve complex problems that are beyond the capabilities of classical computers.

Finally, IBM should continue to invest in cybersecurity to protect its customers' data and systems. Cybersecurity threats are increasing in frequency and sophistication, and IBM needs to stay ahead of the curve to protect its customers.

In conclusion, IBM's technology management practices are guided by best practices that include a focus on innovation, collaboration, and customer-centricity. The company's current technology infrastructure and capabilities include hybrid cloud, AI, blockchain, quantum computing, and cybersecurity. To maintain its leadership position in key technology areas, IBM should invest in hybrid cloud and AI, focus on developing its blockchain and quantum computing capabilities,

\newpage